\textit{MSF: Modulated Sub-graph Finder}

### 2018-03-19 MSF_Paper_FA.tex
.

High throughput sequencing techniques have been widely used to yield
the differentially expressed genes (DEG)~\cite{DEG}. To this end,
changes in transcript abundance are measured, e.g.~by next generation
sequencing techniques, and interpreted as an indicator of differential
expression of genes. DEGs can be used to get
insights into the mechanism underlying differences between conditions of samples, such as
healthy versus diseased. Differential gene
expression analysis (DGEA) informs about the magnitude of expression changes
between the conditions which are the log fold change, the sign of log fold change and the confidence level
of observing an authentic change, often expressed as
\textit{p}-value. These DEGs are
then used to extract meaningful insights, for example the genes that
could be important for a particular condition or maybe the target gene
of any infection or disease. Out of all high throughput analysis
methods currently in use, pathway-based analysis has become an
important tool to further interpret the results of a DGEA and to
acquire understandings of the perturbations in a biological
system. Biological pathways are sets of genes contained in a functional
unit. DEGs help to identify pathways or networks that may be altered
during a change of condition providing important information about
diseases and its treatment process~\cite{Khatri2012}. Pathway-based
methods use the predefined pathways or networks such as
KEGG~\cite{Kegg} and Reactome~\cite{Reactome}, the expression
measurements of the genes obtained from DGEA in combination with statistical methods and algorithms to
identify specifically modulated pathways and processes~\cite{Campos}.

@@

	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Git/MSF_Paper/Tgfb1} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Git/MSF_Paper/TGFBstep1}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Git/MSF_Paper/TGFBstep2} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Git/MSF_Paper/TGFBstep3}
		\caption{}
	\end{subfigure}
	\caption{Overview of \texttt{MSF} process showing the steps to identify the modulated sub-graphs. (a) showing a network of genes with green nodes as genes with \textit{p}-values $< $ 0.05, and blue nodes are genes with \textit{p}-values $>$ 0.05, (b) the genes circled red show the two initial modulated sub-graphs, sub-graph1 found one with M,K,C and the second modulated sub-graph2 S,V,T, (c) shows the modulated sub-graph1 being extended to M,K,C,A,D, (d) shows both the modulated sub-graphs merged with the addition of 3 genes Z,W,P.}
			\end{minipage}
}
\end{figure*}

\begin{figure*}
	\centering
	\fbox{
		\begin{minipage}{17 cm}
	\includegraphics[width=1.4\linewidth]{Git/MSF_Paper/newestMergedNetwork}
	\caption{Shows connected modulated sub-graphs from 6hpi, where nodes are genes and edges are the interactions. The node coloring represents the predefined KEGG pathways referring to the nodes in the legend, the edges are from Reactome. Important genes to EBOV infection as from literature are enlarged in the graph. The signal flow depicted in the graph is explained in the text.}
		\end{minipage}
}
\end{figure*}

\begin{figure*}[p]
	\centering
	\fbox{
		\begin{minipage}{17 cm}
			\includegraphics[width=16cm]{Git/MSF_Paper/DEGvsMSF2}
			\caption{Graph shows the percentage of DEG analysis genes and MSF identified sub-graph genes recall rates 100 times for the three different time points after the addition of Poisson distributed noise.}
			\label{label}
		\end{minipage}
	}
\end{figure*}

>>>>

High throughput sequencing techniques have been widely used to yield
the differentially expressed genes (DEG)~\cite{DEG}. To this end,
changes in transcript abundance are measured, e.g.~by next generation
sequencing techniques, and interpreted as an indicator of differential
expression of genes. DEGs can be used to get
insights into the mechanism underlying differences between conditions of samples, such as
healthy versus diseased. Differential gene
expression analysis (DGEA) informs about the magnitude of expression changes
between the conditions which are the log fold change, the sign of log fold change and the confidence level
of observing a authentic change, often expressed as
\textit{p}-value. These DEGs are
then used to extract meaningful insights, for example the genes that
could be important for a particular condition or maybe the target gene
of any infection or disease. Out of all high throughput analysis
methods currently in use, pathway-based analysis has become an
important tool to further interpret the results of a DGEA and to
acquire understandings of the perturbations in a biological
system. Biological pathways are sets of genes contained in a functional
unit. DEGs help to identify pathways or networks that may be altered
during a change of condition providing important information about
diseases and its treatment process~\cite{Khatri2012}. Pathway-based
methods use the predefined pathways or networks such as
KEGG~\cite{Kegg} and Reactome~\cite{Reactome}, the expression
measurements of the genes obtained from DGEA in combination with statistical methods and algorithms to
identify specifically modulated pathways and processes~\cite{Campos}.

@@

	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Tgfb1.png} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{TGFBstep1.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{TGFBstep2.png} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{TGFBstep3.png}
		\caption{}
	\end{subfigure}
	\caption{Overview of \texttt{MSF} process showing the steps to identify the modulated sub-graphs. (a) showing a network of genes with green nodes as genes with \textit{p}-values $< $ 0.05, and blue nodes are genes with \textit{p}-values $>$ 0.05, (b) the genes circled red show the two initial modulated sub-graphs, sub-graph1 found one with M,K,C and the second modulated sub-graph2 S,V,T, (c) shows the modulated sub-graph1 being extended to M,K,C,A,D, (d) shows both the modulated sub-graphs merged with the addition of 3 genes Z,W,P.}
			\end{minipage}
}
\end{figure*}

\begin{figure*}
	\centering
	\fbox{
		\begin{minipage}{17 cm}
	\includegraphics[width=1.4\linewidth]{newestMergedNetwork.png}
	\caption{Shows connected modulated sub-graphs from 6hpi, where nodes are genes and edges are the interactions. The node coloring represents the predefined KEGG pathways referring to the nodes in the legend, the edges are from Reactome. Important genes to EBOV infection as from literature are enlarged in the graph. The signal flow depicted in the graph is explained in the text.}
		\end{minipage}
}
\end{figure*}

\begin{figure*}[p]
	\centering
	\fbox{
		\begin{minipage}{17 cm}
			\includegraphics[width=16cm]{DEGvsMSF2.png}
			\caption{Graph shows the percentage of DEG analysis genes and MSF identified sub-graph genes recall rates 100 times for the three different time points after the addition of Poisson distributed noise.}
			\label{label}
		\end{minipage}
	}
\end{figure*}
